### 2016-07-25 Docs/managing_jobs/managingjobs.tex
update yt @ NERSC instructions

\item Intel 16.x currently has issues with the linear solvers in \boxlib\
  and should be avoided.

@@

This way of building \yt\ installs it's own python and support
libraries in a directory, {\tt yt-conda}.  You need to make sure that
your start-up files (typically {\tt .bashrc.ext} at NERSC) don't {\tt
  module load} python or any python libraries, as this will interfere
with the conda installation.  The install script will direct you to
add the install location to your path.

At the moment, it seems that this does not actually build the yt source,
so a second step is needed, in {\tt yt-conda/bin/src/yt-hg}, do
\begin{verbatim}
python setup.py develop --user
\end{verbatim}

@@

>>>>

\item Intel 16.0.0 and 16.0.1 have issues compiling the linear solvers
  in \boxlib\ and should be avoided.

  Intel 16.0.2 works fine.

@@

This way of building \yt\ installs it's own python and support
libraries in a directory, {\tt yt-conda}.  {\bf Important: } You need
to make sure that your start-up files (typically {\tt .bashrc.ext} at
NERSC) don't {\tt module load} python or any python libraries, as this
will interfere with the conda installation.  The install script will
direct you to add the install location to your path.

@@

If you want to keep up with the development version of \yt, then you
can update the source in {\tt yt-conda/bin/src/yt-hg}, using:
\begin{verbatim}
hg pull
hg update yt
\end{verbatim}
and then rebuild it via:
\begin{verbatim}
python setup.py develop --user
\end{verbatim}
